---
title: "MET analysis 2020"
author: "Johanne Nedergård"
date: "16/4/2020"
output: pdf_document
---

##Load and preproces 2020 data
```{r}

# code borrowed from Mikkel Wallentin

MET2020 <- read_csv('met_data.csv')



MET2020<-MET2020[1:28,]
colnames(MET2020)[3] <- c('ID')
MET2020$ID<-as.numeric(MET2020$ID)
MET2020$ID[5]<-MET2020$ID[5]/10

#Find correct responses for Melody
melcor1=c("NO","YES","YES","NO","NO","YES","YES","NO","NO","YES","YES","NO","YES")
melcor2=c("YES","YES", "NO","YES","NO","YES","NO","NO","NO","NO","NO","NO","NO")
melcor3=c("YES","YES", "NO","YES","YES","YES","YES","NO","YES","NO","YES","YES","NO")
melcor4=c("YES","NO","YES","NO","YES","NO","NO","NO","YES","YES","NO","NO","YES")
melcor=c(melcor1,melcor2,melcor3,melcor4)
mel=MET2020[,11:62]
n=nrow(mel)
melcomb=matrix(nrow=n,ncol=52)
for (xx in 1:n){
  melcomb[xx,]=(mel[xx,]==melcor)}
melscore <- apply(melcomb, 1, sum)

METscore<-data.frame(melscore)

#rm('melcor1','melcor2','melcor3','melcor4','melcomb','melscore','n','xx','mel','melcor')

#Find correct responses for Rhythm
rytcor1=c("NO","NO","YES","NO","NO","YES","YES","YES","YES","NO","YES","NO","NO")
rytcor2=c("YES","NO","YES","NO","YES","NO","NO","NO","NO","YES","YES","YES","YES")
rytcor3=c("YES","NO","NO","YES","NO","YES","NO","NO","YES","NO","YES","YES","NO")
rytcor4=c("YES","NO","NO","YES","YES","YES","NO","YES","NO","YES","YES","NO","NO")
rytcor=c(rytcor1,rytcor2,rytcor3,rytcor4)
ryt=MET2020[,65:116]
n=nrow(ryt)
rytcomb=matrix(nrow=n,ncol=52)
for (xx in 1:n){
  rytcomb[xx,]=(ryt[xx,]==rytcor)}
rytscore <- apply(rytcomb, 1, sum)

METscore$rytscore<-rytscore
#Clean up
rm('rytcor1','rytcor2','rytcor3','rytcor4','rytcomb','rytscore','n','xx','ryt','rytcor')
```


###Prepare additional variables
```{r}
METscore$totscore<-METscore$melscore+METscore$rytscore
METscore$diffscore<-METscore$melscore-METscore$rytscore
METscore$digit<-MET2020$'What was your forward digit span?'
METscore$musician<-factor(MET2020$'Are you currently playing an instrument (min. one hour per week)?',labels=c('non','musician'))
METscore$ID<-factor(MET2020$ID)
METscore$age<-MET2020$'Your age in years'
#METscore$class<-factor(MET2020$class)
```



##Exploring the data: Descriptive stats
```{r}
# e.g. summary(METscore)
# also descriptive stats on different components of the MET (and digit span) for groups of participants, e.g. musicians and non-musicians
```

###Making histograms and QQ plots for each outcome variable

```{r}
# CHECK
hist(METscore$melscore)
hist(METscore$rytscore)
hist(METscore$digit)

library(ggplot2)
qqnorm(METscore$melscore)
qqnorm(METscore$rytscore)
qqnorm(METscore$digit)

#QQ plots with confidence intervals
library(car)
qqPlot(METscore$melscore)
qqPlot(METscore$rytscore)
qqPlot(METscore$digit)

```

###Boxplots for each outcome meassure as a function of group.

```{r}
library(ggplot2)

# make plots exploring the different DVs (digit span, rhythm score, melody score) as a function of group

```
##Statistical analysis

####-e.g. Student's t-test of difference between musicians and non-musicians
```{R}

# test here

```


###Plot Melody score against Rhythm score

```{r}
library(ggplot2)

# see if rhythm score and melody score are correlated

```

##Statistical analysis

####e.g. Pearson correlation between melody score and rhythm score
```{R}

# also test if they are correlated

```


###Plot digit span against MET score

```{r}
library(ggplot2)

# plot to see if digit span and MET score are related

```

##Statistical analysis

####Pearson correlation between digitspan and MET score
```{R}

# again also test it

```